Calls for Service During 2021 Compared to Pre-Pandemic Forecast - Incident Type

### 2021-06-07 output/forecast_plots.Rmd
updates
Updated Forecast

---
title: "Untitled"
author: ""
date: "23/04/2021"
output: html_document
---

@@

```{r load data, include=FALSE}
call_forecasts <- read_rds(here::here("output/call_forecasts.Rds"))

@@

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

Majority of calls are significantly different from the forecast data.

@@

```{r Admin}
forecast_chart(call_forecasts, "Advice/Directions/Admin")
```
Nine time periods fall above of the conifdence intervals, mainly following the first UK lockdown

@@

```{r Alarms}
forecast_chart(call_forecasts, "alarms")
```

Some significant differences between forecast data

@@

Two points could be considered significantly different from the forecast

@@

Over 20 point are considered signifcantly different form the forecast data as expected, mainly following the first lockdown and second lockdown. Supports literature with increase in ASB due to breaking restriction rules. Interesting to note the reduction of points outside the confidence intervals from the first lockdown to the second lockdown.

@@

General decrease of commercial calls with noticable difference following the first lockdown ending

@@

Majority of the calls are significantly different form the forecast, with a sharper reduction at the end of the second lockdown period

@@

Actual calls are general lower than the forecast data but nothing too noticable as only one point is signifcantly different from the forecast

@@

Sharp spikes of siginifcance difference among each time period, constrasts siginficantly to forecasted seasonality

@@

Why are confidence intervals missing?

@@

Actual calls tend to typically not differ too much from the forecast data. However, with those that do we see 5 points below the confidence intervals before the first lockdown ends and then 2 points higher than the confidence intervals after the seocnd lockdown begins

@@

Actual calls from conerns of saftey fall below the lower 95% CIs during the first lockdown, but then increase as restrictions are relieved,

@@

## Distraction Burglary

```{r Distraction Burglary}
forecast_chart(call_forecasts, "Distraction Burglary")
```

No plot produced - error message 'Error in unit(x, default.units) : 'x' and 'units' must have length > 0'

@@

Overall the actual calls for domestic incident fall above the upper bound of the 95% CI, mainly following the start of the first lockdown. This is reflective of literature with more people remaining at home

@@

During the start of the first UK lockdown there is a significant increase of drug related offenses. Moreover, where we expect to see a spike during the first lockdown ending, there is in fact a significant decrease of crime.

@@

Overall, no significant differences in firearms offenses (some exception following stage 2). However, the overal patterns of actual crimes seems to differ from the forecast trend within the upper and lower bounds of the confidence intervals.

@@

9 time points are seen as significantly different from the forecast, happening from the first UK Covid case up until the ending of the first lockdown. Most of these points fall below the lower bound of the CIs, could be reflective of less opportunity for Fraud to happen given the closures of retails and businesses

@@

During the the first UK covid case and the first lockdown, there are two points above the forecasted data. There is also a general increase of hate incidents (withtin the CIs but still high) following the fist lockdown ending - reflective of increasd biased and prejudice to Asian communities,

@@

Siginificantly lower levels of highway disruption from the first lockdown as a result of less people travelling. Also supported by the small increase after the first lockdown ended (3)

@@

Significant differences again following the first lockdown. Supported by literature with more children being at home and less opportunity for 'juvenile runaways' but also for high risk individuals

@@

Small changes to admin calls following the first lockdown as expected with a decrease of weekly calls. However, typically the trends follows the overal forecast pattern

@@

Actual calls generally fall below the forecasted data as expected. However there is one increased signifcant difference following the second lockdwon ending

@@

Interestingly, actual calls from police generated calls fall above the confidence interval throughout all 5 key dates.

@@

@@

Actual calls of road related traffic offences fall far below the forecasted data. Again, this is expected due to less people traveling during the restrictions put in place. However, could also be due to less officers working as result having the virus.

@@

During time period one, there was a high spike in actual calls of robbery where the first UK covid case happened - why is this? We also see a break in the seasonality and more random fluctuations throughout the five key dates

@@

During the first lockdown cases of sexual offences decreased and fell below the 95% confidence intervals, trends however return to normal follwoing the end of the lockdown. Interesting to note that this pattern somewhat consistent across the second lockdown with a decreasing trend, however the drop is not as prominent as it is seen in the first lockdown - restrictions possibly broken more regulary

@@

Significant differences following the first lockdown as would be expected due to closure of retail and buisnesses. Arguably different seaonality patterns as well

@@

Two time periods are seen as significantly differnt from the forecast which happens at the start of the first UK lockdown, this could be as a result of increase Coronavirus cases or reduced information around the virus, Results tend to fall back to normal soon after.

@@

No significant differnces in suspicious activity calls.

@@

Arguable differences in actual calls compared to forecast data - why is that point 'true' even though its within the confidence intervals in time period 3?

@@

General decrease of motor theft following the first uk lockdown. However, trends seem to follow the same seaonsal pattern just at a lower weekly rate

@@

General decrease of theft other following the first uk lockdown

@@

General decrease following the first lockdown, trends seems to increase soon after but still can be considered significantly different from the forecast data

@@

Following the first lockdown there is a general decrease of violence and harassment compared to the forecast data

@@

Concluding Thoughts; Most significant changes in calls happen following the first U.K lockdown, these patterns of change are also reflected in the second lockdown but at a much lower rate.

Some errors: 
- no plots produces for distraction burglary and property/lost found 
- confidence intervals look different in minor injuries

>>>>

---
title: "Calls for Service During 2021 Compared to Pre-Pandemic Forecast - Incident Type"
author: "Matt Ashby, Nadia Kennar, Reka Solymosi"
date: "23/04/2021"
output: html_document
---

@@

```{r load data, include=FALSE}
call_forecasts <- read_rds(here::here("output/call_forecasts.Rds"))
#call_forecasts <- read_rds("Z:\\call_forecasts.Rds")

@@

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

Majority of calls are significantly different from the forecast data. Less weekly calls received with a decreasing trend

@@

```{r Admin}
forecast_chart(call_forecasts, "Advice/Directions/Admin")
```

No significant differences in the weekly call counts from Admin. Nine time periods fall above of the conifdence intervals, mainly following the first UK lockdown

@@

```{r Alarms}
forecast_chart(call_forecasts, "alarms")
```
No significant differences between actual calls and forecast data

@@

No significant differences between actual calls and forecast data

@@

Over 20 point are considered significantly different form the forecast data as expected, mainly following the first lockdown and second lockdown. Supports literature with increase in ASB due to breaking restriction rules. Interesting to note the reduction of points outside the confidence intervals from the first lockdown to the second lockdown.

@@

General decrease of commercial calls with little significant difference following the ending of first lockdown

@@

Majority of the calls are significantly different form the forecast, with a sharper reduction at the end of the second lockdown period. However, to say there is a clear difference in the trend is questionable

@@

Actual calls are general lower than the forecast data but nothing too noticeable as only one point is significantly different from the forecast

@@

No significant differences in the trend between actual calls and foretasted data. A few points do sit above and below but this is expected with calls to service

@@

Foretasted trend seems to follow actual trend, nothing too different to note

@@

Actual calls tend do not differ too much from the forecast data. With only, 5 points below the confidence intervals before the first lockdown ends and then 2 points higher than the confidence intervals after the second lockdown begins

@@

Actual calls from concerns of safety rarely fall below the lower 95% CIs; no significant differences in the plot

@@

@@

Only a few of the actual calls recorded for domestic incident fall above the upper bound of the 95% CI, mainly following the start of the first lockdown. Might have expected to see more calls falling outside the predicted data with literature stating that more people remain home?

@@

Small change in actual calls received during the start of the first lockdown compared to forecast data. During the start of the first UK lockdown there is a significant increase in drug related offenses.

@@

The overall patterns of actual crimes do not differ that significantly from the forecast results with the majority of points remaining within the upper and lower bounds of the confidence intervals.

@@

9 time points are seen as significantly different from the forecast, happening from the first UK Covid case up until the ending of the first lockdown. Most of these points fall below the lower bound of the CIs, could be reflective of less opportunity for Fraud to happen given the closures of retails and businesses. However, with inconsistent changes in the trend a clear conclusion can't be drawn

@@

Overall actual calls do not significant differ from forecasted data. During the the first UK Covid case and the first lockdown, there are two points above the forecast data. There is also a general increase of hate incidents (within the CIs but still high) following the fist lockdown ending - reflective of increased biased and prejudice to certain communities

@@

Significantly lower levels of highway disruption from the first lockdown as a result of less people traveling. Also supported by the small increase after the first lockdown ended (3)

@@

Significant differences again following the first lockdown. Supported by literature with more children being at home and less opportunity for 'juvenile runaways'.

@@

Small changes to admin calls following the first lockdown as expected with a decrease of weekly calls. However, typically the trends follows the overall forecast pattern

@@

Actual calls generally fall within the CIs - no siginificant differences

@@

Interestingly, actual calls from police generated calls fall above the confidence interval throughout all 5 key dates. However, no clear trend in the changes instead some random fluctuations

@@

No obvious diferences between actual calls and forecasted data.

@@

Actual calls of road related traffic offenses typically fall below the forecasted data. Again, this is expected due to less people traveling during the restrictions put in place and a reduction in able employees.

@@

During time period one, there was a high spike in actual calls of robbery where the first UK Covid case happened - why is this? We also see a break in the seasonality and more random fluctuations throughout the five key dates. Arguably nothing too different from the forecasted data

@@

During the first lockdown cases of sexual offenses decreased and fell below the 95% confidence intervals, trends however return to normal following the end of the lockdown. No signifcant differences from the forecast data

@@

Significant differences following the first lockdown as would be expected due to closure of retail and businesses. Arguably different seasonality patterns as well

@@

Two time periods are seen as significantly different from the forecast which happens at the start of the first UK lockdown, this could be as a result of increase Covid-19 cases or reduced information around the virus, Results tend to fall back to normal soon after. Overall, actual calls are not significantly different from forecast

@@

No significant differences in suspicious activity calls.

@@

Arguable differences in actual calls compared to forecast data.

@@

General decrease of motor theft following the first uk lockdown. However, trends seem to follow the same seasonal pattern just at a lower weekly rate.

@@

General decrease of theft other following the first uk lockdown. Overall, the trend from actual calls are significantly different from forecast data

@@

General decrease following the first lockdown, trends seems to increase soon after but still can be considered significantly different from the forecast data a a decreased weekly rate

@@

Following the first lockdown there is a general decrease in weekly counts of violence and harassment compared to the forecast data.

@@

Concluding Thoughts; Most significant changes in calls to service happen following the first U.K lockdown, these patterns of change are also reflected in the second lockdown but at a much lower weekly crime rate.
